Switch equivalence and weak prime domains for fusions

### 2023-10-10 fusione.tex
unicità

\title{Switch equivalence and weak prime domains for fusions}

@@

	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rule as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.

@@

\begin{definition}
	The \emph{DPO-derivation category} of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
\end{definition}
\begin{remark}
Derivations, being paths in a graph, can be concatenate: given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their \emph{concatenation} $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
\[\dder{E}_i:=\begin{cases}
	\dder{D}_i & i \leq n\\
	\dder{D}'_{i-(n+1)} & n< i 
\end{cases}\]

@@

Given two decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ with  $\der{D}=\{\dder{D}_i\}_{i=0}^n$, $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$, we will say that $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for every index $i$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
\[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_0} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]

@@

\begin{definition}
Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$. If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation}  $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$as $((\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}'), \alpha, \omega')$.
\end{definition}

\begin{remark}\label{rem:lgt}
	contenuto...
\end{remark}

@@

\begin{proof}
	contenuto...\qed 
\end{proof}

\begin{definition}
	contenuto...
\end{definition}

\begin{definition}
	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  graph $\gpi$ is the (large)  directed graph having as vertices isomorphism classes of objects of $\X$ and in which an edge between $[G]$ and $[H]$ is the equivalence class $[\der{D}]_a$ of derivation $\der{D}$ between $G$ and $H$.	
\end{definition}

\begin{remark}
	contenuto...
\end{remark}
\subsection{Consistent permutations}

@@

	To see that such $c$ is unique, suppose that $c':\tpro{D}\to C$ is given such that
	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
	Then, for every $X\in \Delta(\der{D})$ we have
	\begin{align*}
		c'\circ \iota_X &= \begin{cases}
			c'\circ p_1\circ \iota'_{X} & X\in \Delta(\der{D}')\\
			c'\circ p_2\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			c'\circ \iota_{D_j} & X=D_j
		\end{cases}\\&=\begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
		c'\circ p_1 \circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&= \begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			b\circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&=c_X\\&=c\circ \iota_X
	\end{align*}
	allowing us to deduce that $c'=c$.	\qed 	
	\end{enumerate}
\end{proof}
\begin{corollary}\label{cor:ele}
	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$. Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.  Consider two arrows $a:T\to G_j$, $b:T\to G_k$. If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$, 
	then  there exist arrow $c:T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
	\end{corollary}
\begin{proof} We split the cases.
	\begin{itemize}
		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
		\[\xymatrix@C= 40pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]^{p_2} \\ &G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ &\lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram above. 
			\[\xymatrix@C=30pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ &G_j \ar[d]^{\iota'_{G_j}}\\ &\lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Such rectangle is an $\mathcal{M}$-pushout and the thesis follows from \Cref{prop:pbpoad}. \qed
	\end{itemize}
\end{proof}

@@

\begin{definition}
	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.  Take two non-empty derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with the same length with their associated sequences of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$. A permutation $\sigma:n+1\to n+1$  is called a \emph{consistent permutation} between $\der{D}$ and $\der{D}'$, if for every $i\in n+1$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists an isomorphism $\xi:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
\end{definition}

\begin{remark}
The commutativity of the two rectangles above, is equivalent to the commutativity of the following bigger diagram.		
\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_{\sigma(i)}} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_{\sigma(i)}} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_{\sigma(i)}} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota'_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota'_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota'_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi}&& \lpro \der{D}' \rpro}\]

Indeed,  to prove the commutativity of the central pentagon we can compute to get:
\begin{align*}
	\xi \circ \iota_{D_i}\circ k_i&=\xi \circ \iota_{G_{i}} \circ f_i\\&= \xi \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
\end{align*}
\end{remark}

\begin{remark}\label{rem:coproj}
Notice that, in particular, the previous diagram entails
		\[\xi \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
\end{remark}

\begin{example} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ be two abstraction equivalent non-empty derivations. Then the identity permutation $\id{n+1}$ is a consistent permuation between them. In such a case $\xi$ is simply the isomorphism induced by the $\{\phi^i\}_{i=0}^n$.
\end{example}

@@

\begin{proposition}\label{prop:sep}
	contenuto...
\end{proposition}
\begin{proof}
	contenuto...
\end{proof}

@@

\begin{corollary}\label{cor:unique}
	contenuto...
\end{corollary}

>>>>

\title{Switch equivalence and weak prime domains for fusions}
\author{Paolo Baldan \and Davide Castelnovo  \and  Andrea Corradini  Fabio Gadducci}

@@

	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.

@@

\begin{definition}
	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
\end{definition}
\begin{remark}
Derivations, being paths in a graph, can be concatenate: given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their \emph{concatenation} $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
\[\dder{E}_i:=\begin{cases}
	\dder{D}_i & i \leq n\\
	\dder{D}'_{i-(n+1)} & n< i 
\end{cases}\]

@@

Given two decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ with  $\der{D}=\{\dder{D}_i\}_{i=0}^n$, $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$, we will say that $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for every index $i$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
\[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_1} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]

@@

\begin{definition}
Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$. If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation}  $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$ as $((\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}'), \alpha, \omega')$.
\end{definition}

\begin{remark}\label{rem:lgt}
	Given two composable decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$  such that $\der{D}$ and $\der{D}'$ have  length $n$ and $m$, respectively, then $(\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}')$ has length $n+m$.
\end{remark}

@@

\begin{proof}
	To fix the notation, let $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ be given by
	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^m \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^m\]
	Let also $\{\phi^i\}_{i=0}^n$ and $\{\varphi^i\}_{i=0}^m$ be families of abstract equivalences between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively. For every $i\in [0, n+m-1]$ define 
	\[\psi^{i}:=\begin{cases}
		\phi^i & i< n\\
		(\phi^n_1, \phi^n_2, \id{\pi(H)}) & i=n\\
		(\id{\pi(E)}, \varphi^{0}_2, \varphi^{0}_3) & i=n+1\\
		\varphi^{i-n+1} & i>n+1
	\end{cases}\] 
Notice suppose that $h_n:R_n\to H, h_n:R_n\to H'$ are the back-matches of $\der{D}_n$ and $\der{D}'_n$ and that the following diagram is given
	\[\xymatrix@C=40pt@R=10pt{ &&&R_n\ar[dddr]^{h'_n} \ar[dddl]_{h_n}|(.67)\hole\\&&K_n \ar[dl]_{l_n} \ar[ur]^{r_n}\ar[dddr]^{k'_n} \ar[dddl]_{k_n}|(.67)\hole\\&L_n\ar[dddr]^(.4){m'_n} \ar[dddl]_(.4){m_n}\\&&H \ar[rr]^{\phi^n_3} && H'\\ & D_n \ar[ur]_(.7){g_n} \ar[rr]^{\phi^n_2} \ar[dl]_{f_n}&& D'_n \ar[ur]_{g'_n}\ar[dl]^{f'_n}\\ G_{n} \ar[rr]_{\phi^n_1} && G'_n}\]
Then we have
\begin{align*} 
	\id{\pi(H)}\circ \omega^{-1} \circ h_n&=(\omega')^{-1}\circ \phi^n_3 \circ \omega \circ \omega^{-1} \circ h_n\\&=(\omega')^{-1}\circ \phi^n_3  \circ h_n\\&=(\omega')^{-1}  \circ h'_n
\end{align*} 
and 
\begin{align*} \id{\pi(H)}\circ \omega^{-1} \circ g_n  &=(\omega')^{-1}\circ \phi^n_3 \circ \omega \circ \omega^{-1}\circ g_n\\&=(\omega')^{-1}\circ \phi^n_3\circ g'_n\\&=(\omega')^{-1}\circ g'_n\circ \phi^n_2\end{align*}
Therefore $\psi^n$ is an abstract equivalence between $\dder{D}_n*\omega^{-1}$ and $\dder{D}_n'*(\omega')^{-1}$.

Similarly, if $\hat{m}_0:\hat{L}_0\to E, \hat{m}'_0:L'_0\to E'$ the matches of $\der{E}_0$, $\der{E}'_0$, we can consider the diagram
\[\xymatrix@C=40pt@R=10pt{ &&&\hat{R}_0\ar[dddr]^{\hat{h}'_0} \ar[dddl]_{\hat{h}_0}|(.67)\hole\\&&\hat{K}_0 \ar[dl]_{\hat{l}_0} \ar[ur]^{\hat{r}_0}\ar[dddr]^{k'_0} \ar[dddl]_{\hat{k}_0}|(.67)\hole\\&\hat{L}_n\ar[dddr]^(.4){\hat{m}'_0} \ar[dddl]_(.4){\hat{m}_0}\\&&\hat{G}_1 \ar[rr]^{\varphi^0_3} && \hat{G}'_1\\ & \hat{D}_0 \ar[ur]_(.7){\hat{g}_0} \ar[rr]^{\varphi^0_2} \ar[dl]_{\hat{f}_0}&& \hat{D}'_0 \ar[ur]_{\hat{g}'_0}\ar[dl]^{\hat{f}'_0}\\ E \ar[rr]_{\varphi^0_1} && E'}\]
and computing we get
\begin{align*}
	\id{\pi(E)}\circ \alpha^{-1} \circ \hat{m}_0&=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1} \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \varphi^0_1  \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \hat{m}'_n
\end{align*}
together with
\begin{align*} \id{\pi(E)}\circ \alpha^{-1}\circ \hat{f}_0  &=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1}\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \varphi^0_1\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \hat{f}'_0\circ \varphi^0_2\end{align*}
The previous two identities show that $\psi^{n+1}$ is an abstract equivalence between $\dder{E}_0$ and $\dder{E}'_0$. By hypothesis $\pi(H)=\pi(E)$ and, moreover, we have
	\[\begin{split}
		\psi^{0}_1\circ \alpha &= \phi^0_1\circ \alpha \\&= \alpha'
	\end{split}\qquad \begin{split}
	\psi^{n+m-1}_3\circ \xi &=\varphi^m_3\circ \xi \\&= \xi'
	\end{split}\]
Therefore the thesis now follows.	\qed 
\end{proof}

\begin{definition}
	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
	\begin{itemize}
		\item objects are isomorphism classes of objects of $\X$;
		\item a non-identity arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_a$ of a decorated derivation between $G'$ and $H'$ for some $G'$ and $H'$ such that $\pi(G')=G$ and $\pi(H')=H$;
		\item composition is concatenation of abstract decorated derivations;
		\item identities are added formally.
	\end{itemize}
\end{definition}

\subsection{Consistent permutations}

@@

	To see that such $c$ is unique, suppose that $c':\tpro{D}\to C$ is given such that
	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
	Then, for every $X\in \Delta(\der{D})$ we have
	\begin{align*}
		c'\circ \iota_X &= \begin{cases}
			c'\circ p_1\circ \iota'_{X} & X\in \Delta(\der{D}')\\
			c'\circ p_2\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			c'\circ \iota_{D_j} & X=D_j
		\end{cases}\\&=\begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
		c'\circ p_1 \circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&= \begin{cases}
		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
			b\circ \iota'_{G_j} \circ f_j  & X=D_j
		\end{cases}\\&=c_X\\&=c\circ \iota_X
	\end{align*}
	allowing us to deduce that $c'=c$.	\qed 	
	\end{enumerate}
\end{proof}
\begin{corollary}\label{cor:ele}
	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$. Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.  Consider two arrows $a:T\to G_j$, $b:T\to G_k$. If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$, 
	then  there exist arrow $c:T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
	\end{corollary}
\begin{proof} We split the cases.
	\begin{itemize}
		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
		\[\xymatrix@C= 40pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]^{p_2} \\ &G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ &\lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram below is a pushout. 
			\[\xymatrix@C=30pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ &G_j \ar[d]^{\iota'_{G_j}}\\ &\lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\] 
		Point $2$ of \Cref{lem:colim} entails that $\iota'_{G_j}$ is in $\mathcal{M}$, and so is $f_j$ as it is the pushout of $l_j$. Thus the rectangle we are considering is an $\mathcal{M}$-pushout and the thesis follows again from \Cref{prop:pbpoad}. \qed
	\end{itemize}
\end{proof}

@@

\begin{definition}\label{def:permcon}
	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.  Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ such that
	\begin{itemize}
		\item $\der{D}$ and $\der{D}'$ have the same length;
		\item if  $\der{D}$  is a derivation between $G$ and $H$ amd $\der{D}'$ one between $G'$ and $H'$, then $G\simeq G'$ and $H\simeq H'$.
	\end{itemize}

	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated squence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma:[0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
	\[\xymatrix{\pi(G)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G \ar[r]^{\iota_{G}} &\tpro{D} \ar[d]^{\xi}&   \pi(H) \ar[r]^{\omega} \ar[d]_{\omega'} & H \ar[r]^{\iota_H} &\tpro{D} \ar[d]^{\xi}\\ G' \ar[rr]_{\iota'_{G'}} & &\lpro \der{D}' \rpro& H' \ar[rr]_{\iota'_{H'}} & &\lpro \der{D}' \rpro}\]
\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
\end{definition}

\begin{remark}
The commutativity of the last two rectangles in \Cref{def:permcon}, is equivalent to the commutativity of the following bigger diagram.		
\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_{\sigma(i)}} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_{\sigma(i)}} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_{\sigma(i)}} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota'_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota'_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota'_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi_\sigma}&& \lpro \der{D}' \rpro}\]

Indeed,  to prove the commutativity of the central pentagon we can compute to get:
\begin{align*}
	\xi_\sigma \circ \iota_{D_i}\circ k_i&=\xi_\sigma \circ \iota_{G_{i}} \circ f_i\\&= \xi_\sigma \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
\end{align*}
\end{remark}

\begin{remark}\label{rem:coproj}
Notice that, in particular, the previous diagram entails
		\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
\end{remark}

\begin{remark}\label{rem:comp} Consistent permutations can be composed. Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
	\[\xymatrix@C=18pt{ & G \ar[rr]^{\iota_{G}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  H \ar[rr]^{\iota_H} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G' \ar[rr]^{\iota'_{G'}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi(H)\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & H' \ar[rr]^{\iota'_{H'}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}  \ar[rr]_{\hat{\iota}_{\hat{G}}}&& \lpro \hat{\der{D}}\rpro  && \hat{H} \ar[rr]_{\hat{\iota}_{\hat{H}}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
\end{remark}

\begin{example} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$. Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them. In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any family $\{\phi^i\}_{i=0}^n$ witnessing $(\der{D}, \alpha, \omega)\equiv^a (\der{D}', \alpha', \omega')$.
\end{example}

@@

@@
